Packaging research artefacts with RO-Crate

### 2022-01-02 latex/ro-crate.tex
cite RFC3987 where mentioned

Definition of language $\mathcal{L}_{\mathit{rocrate}}$:
%
\begin{eqnarray*}
\mathcal{L}_{\mathit{rocrate}} &=& \bigl\{\mathit{Property}(p), \mathit{Class}(c),
\mathit{Value}(x), \mathbb{R}, \mathbb{S} \bigr\}
\\
\mathbb{D} &=& \mathbb{IRI}
\\
\mathbb{IRI} &\equiv& { \text{IRIs as defined in RFC3987} }
\\
\mathbb{R} &\equiv& { \text{real or integer numbers} }
\\
\mathbb{S} &\equiv& { \text{literal strings} }
\end{eqnarray*}

The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$
identifiers \cite{doi:10.17487/rfc3987} (notation \texttt
{<http://example.\noxml{\break}com/>}),\footnote{For simplicity, blank nodes are not included in this formalisation, as RO-Crate
recommends the use of IRI identifiers: \url
{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html\#describing-entities-in-json-ld}.} with additional descriptions using numbers $\mathbb{R}$ (notation
$13.37$) and literal strings $\mathbb{S}$ (notation $\text{``Hello''}$).

>>>>

Definition of language $\mathcal{L}_{\mathit{rocrate}}$:
%
\begin{eqnarray*}
\mathcal{L}_{\mathit{rocrate}} &=& \bigl\{\mathit{Property}(p), \mathit{Class}(c),
\mathit{Value}(x), \mathbb{R}, \mathbb{S} \bigr\}
\\
\mathbb{D} &=& \mathbb{IRI}
\\
\mathbb{IRI} &\equiv& { \text{IRIs as defined in RFC3987 \cite{doi:10.17487/rfc3987}} }
\\
\mathbb{R} &\equiv& { \text{real or integer numbers} }
\\
\mathbb{S} &\equiv& { \text{literal strings} }
\end{eqnarray*}

The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$
identifiers (notation \texttt
{<http://example.\noxml{\break}com/>}),\footnote{For simplicity, blank nodes are not included in this formalisation, as RO-Crate
recommends the use of IRI identifiers: \url
{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html\#describing-entities-in-json-ld}.} with additional descriptions using numbers $\mathbb{R}$ (notation
$13.37$) and literal strings $\mathbb{S}$ (notation $\text{``Hello''}$).
